Paper notes

### 2019-08-09 paper_notes.Rmd
test, ignore
3 functions plot in 1 page

library(Hmisc)
library(ggplot2)

# Here functions that are used.

@@

```{r graph function include=TRUE, echo=FALSE}

@@

x_graph <- rep(seq(0, 8, by = 1),3)
funct_symm <- c(rep("symmetric",9),rep("constant",9),rep("threshold",9))
utility_location <- c(Utility_S,Utility_C,Utility_T)

A <- data.frame(x_graph[c(0:9)],utility_location[c(0:9)],funct_symm[c(0:9)])

A

@@

A_graph <- ggplot(A,aes(x_graph[c(0:9)],utility_location[c(0:9)]))

A_graph + geom_point()

A_graph + geom_point(aes(colour = funct_symm, shape= funct_symm, size = funct_symm)) + scale_size_manual(values = c(4,5,3)) + scale_shape_manual(values = c(19,19,19)) + scale_color_manual(values = c("darkorchid","forestgreen","black"))

@@

```{r overlap_function include=TRUE, echo=FALSE}

@@

S_0 <- c(0,0,0,0,0,NA,NA,NA,NA)
M_1 <- c(NA,NA,NA,NA,1,1,1,1,1)
S_1 <- c(0,0.25,0.5,0.75,1,NA,NA,NA,NA)
M_0 <- c(NA,NA,NA,NA,1,0.75,0.5,0.25,0)  # should be 0.75 and 0.24, I think due to round(U)2 in the function

@@

```{r ethnic utility individual-run include=TRUE, echo=FALSE}

@@

```{r value_similarity, echo=FALSE, }

>>>>

library(Hmisc)
library(ggplot2)
library(gridExtra)
library(ggpubr)
# Here functions that are used.

@@

```{r graph function, include=TRUE, echo=FALSE}

@@

x_graph <- rep(seq(0, 100, by = 12.5),3)
funct_symm <- c(rep("symmetric",9),rep("constant",9),rep("threshold",9))
utility_location <- c(Utility_S,Utility_C,Utility_T)

symmetric <- data.frame(x_graph[c(0:9)],utility_location[c(0:9)],funct_symm[c(0:9)])
constant <- data.frame(x_graph[c(10:18)],utility_location[c(10:18)],funct_symm[c(10:18)])
threshold <- data.frame(x_graph[c(19:27)],utility_location[c(19:27)],funct_symm[c(19:27)])

# symmetric
# constant
# threshold

@@

symmetric_graph <- ggplot(symmetric,aes(x_graph[c(0:9)],utility_location[c(0:9)])) 
constant_graph <- ggplot(constant,aes(x_graph[c(10:18)],utility_location[c(10:18)])) 
threshold_graph <- ggplot(threshold,aes(x_graph[c(19:27)],utility_location[c(19:27)]))

symmetric_plot <- symmetric_graph + geom_point() + theme_bw() + labs(x = "percentage similars",y = "utility for location") + ggtitle("Symmetric Single Peaked \n\r (S=1,M=0) ") + theme(plot.title = element_text(hjust = 0.5))
constant_plot <- constant_graph + geom_point() + theme_bw() + labs(x = "percentage similars",y = "utility for location") + ggtitle("Linear + Constant \n\r (S=1,M=1)") + theme(plot.title = element_text(hjust = 0.5))
threshold_plot <- threshold_graph + geom_point() + theme_bw() + labs(x = "percentage similars",y = "utility for location") + ggtitle("Schelling Threshold \n\r (S=0,M=1) ") + theme(plot.title = element_text(hjust = 0.5))

suppressWarnings(
grid.arrange(symmetric_plot, constant_plot,threshold_plot, ncol= 2,nrow = 2)
)

@@

```{r overlap_function, include=TRUE, echo=FALSE}

@@

S_0 <- c(0,0,0,0,0,NA,NA,NA,NA)
M_1 <- c(NA,NA,NA,NA,1,1,1,1,1)
S_1 <- c(0,0.25,0.5,0.75,1,NA,NA,NA,NA)
M_0 <- c(NA,NA,NA,NA,1,0.75,0.5,0.25,0)

@@

```{r ethnic utility individual-run, include=TRUE, echo=FALSE}

@@

```{r value_similarity, echo=FALSE }
